\documentclass[a4paper, 11pt, oneside]{Thesis-1}

\graphicspath{{Figures/}}

\usepackage[square, numbers, comma, sort&compress]{natbib}
\usepackage{verbatim}
\usepackage{longtable}          % multi-page tables
\usepackage{array}              % extended column definitions
\usepackage{booktabs}           % professional table rules
\usepackage{multirow}           % \multirow in SDG table
\usepackage{colortbl}           % \rowcolor in SDG table
\usepackage[table]{xcolor}      % colour definitions
\usepackage{acronym}            % List of Acronyms
\usepackage{listings}           % Code listings in Appendix
\usepackage{courier}            % Courier font for code
\hypersetup{urlcolor=blue, colorlinks=true}

%% ----------------------------------------------------------------
\begin{document}
\frontmatter

\title  {\bf Asynchronous Sensor Fusion for ISAC Nodes Integrating Wi-Fi Sensing and mmWave Radar}
\authors{\texorpdfstring{\href{mailto:name.22xxxxx@vitstudent.ac.in}{Name1}
         \and \href{mailto:name.22xxxxx@vitstudent.ac.in}{Name2}}{}}
\addresses{\groupname\\\deptname\\\univname}
\date   {April 2026}
\subject{}
\keywords{}

\maketitle

\setstretch{1.0}
\fancyhead{}
\rhead{\thepage}
\lhead{}
\pagestyle{fancy}

%% ----------------------------------------------------------------
%% DECLARATION
%% ----------------------------------------------------------------
\Declaration{

\addtocontents{toc}{\vspace{1em}}

\vspace{0.5cm}

We hereby declare that the report titled {\bf\textit{Asynchronous Sensor Fusion for ISAC Nodes Integrating Wi-Fi Sensing and mmWave Radar}}
submitted by us to the School of Electronics Engineering, Vellore Institute of
Technology, Chennai, in partial fulfilment of the requirements for the award of
{\bf Bachelor of Technology} in {\bf Electronics and Communication Engineering},
is a bonafide record of the work carried out by us under the supervision of
{\bf\textit{Guide Name}}.

We further declare that the work reported in this report has not been submitted
and will not be submitted, either in part or in full, for the award of any other
degree or diploma of this institute or of any other institute or University.

\vspace{1cm}

\noindent
\begin{tabular}{@{}p{7cm}p{7cm}@{}}
Signature of the Student: \dotfill & Signature of the Student: \dotfill \\[1.2cm]
Name \& Reg.\ No.: \dotfill        & Name \& Reg.\ No.: \dotfill        \\[0.8cm]
Date: \dotfill                     & Date: \dotfill                     \\
\end{tabular}

\thispagestyle{empty}
}

\clearpage

%% ----------------------------------------------------------------
%% CERTIFICATE
%% ----------------------------------------------------------------
\Certificate{
\addtocontents{toc}{\vspace{0.5em}}

This is to certify that the project report titled {\bf\textit{Asynchronous Sensor Fusion for ISAC Nodes Integrating Wi-Fi Sensing and mmWave Radar}}
submitted by {\bf\textit{Name(s)} (Reg.\ No.)} to Vellore Institute of Technology,
Chennai, in partial fulfilment of the requirement for the award of the degree of
{\bf Bachelor of Technology} in {\bf Electronics and Communication Engineering}
is a bonafide work carried out under my supervision. The project report fulfils the
requirements as per the regulations of this University and, in my opinion, meets the
necessary standards for submission. The contents of this report have not been submitted
and will not be submitted either in part or in full, for the award of any other degree
or diploma and the same is certified.

\vspace{0.8cm}

\begin{center}
\begin{tabular}{p{6cm} p{6cm}}
\textbf{Supervisor}              & \textbf{Head of the Department}  \\[1.5cm]
Signature: \dotfill              & Signature: \dotfill              \\[0.5cm]
Name: \dotfill                   & Name: \dotfill                   \\[0.5cm]
Date: \dotfill                   & Date: \dotfill                   \\
\end{tabular}
\end{center}

\vspace{0.6cm}

\begin{center}
\begin{tabular}{p{6cm} p{6cm}}
\textbf{Examiner 1}              & \textbf{Examiner 2}              \\[1.5cm]
Signature: \dotfill              & Signature: \dotfill              \\[0.5cm]
Name: \dotfill                   & Name: \dotfill                   \\[0.5cm]
Date: \dotfill                   & Date: \dotfill                   \\
\end{tabular}
\end{center}

\begin{flushright}
(Seal of the School)
\end{flushright}

\thispagestyle{empty}
}

\thispagestyle{empty}
\clearpage

%% ----------------------------------------------------------------
%% ABSTRACT
%% ----------------------------------------------------------------
\addtotoc{Abstract}
\abstract{
\addtocontents{toc}{\vspace{1em}}

A dual-tier asynchronous sensor fusion framework for the integration of radar sensors and wifi-based ieee 802.11mc fine time measurement on low-cost platforms based on the esp32-s3 dual-core platform is introduced in this work. Single-modality systems utilizing millimeter-wave radar provide range resolution sub-foot resolutions and micro-doppler signatures; however, they are blind to identity and fail under line of sight occlusions. Conversely, wifi-based ieee 802.11mc fine time measurements offer MAC address linked identifications with wall penetration capabilities but exhibit spatial variability ranging from approximately 1.5 m to 4.8 m and update rates that are limited to only 1 hz or 2 hz. As a result, standard Kalman filters lock onto stale wifi readings due to the synchronization gap between the two modality systems which causes trajectory step artefacts during target maneuvers.
The two new fusion methods were tested and compared to each other. The dynamic covariance intersection method (dc-i), used an angular vector from the radar system to project one dimensional wifi range into it. dc-i also applied first order hold velocity extrapolation. When using this method as well as age of information penalties for real time inflation of stale sensor covariances, there was a 45\% improvement in mean squared error over dc-i when sensors became occluded. A small edge mlp (11.6~kb, 2,474 float32 params) took a 5x5 sliding window of forward filled features with fresh flags that indicated if feature was fresh or old. It completed inference in 350 ~microsecond windows completely inside the edge device sram, had a test set average absolute error of 0.118~m and euclidean p95 error of 0.555~m. Isolation of both cores --- wifi on core~0, uart parse \& inference on core~1--- eliminated serial buffer corruption. The validation process utilized a matlab/simulink digital twin and python test suite which covered many different type of cases such as; field of view escapes, pillar occlusions, walking around objects and statue mode scenarios.
}

\clearpage

%% ----------------------------------------------------------------
%% ACKNOWLEDGEMENTS
%% ----------------------------------------------------------------
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}

We wish to express our sincere thanks and deep sense of gratitude to our project guide,
\textbf{Dr.~XXXX}, Professor, School of Electronics Engineering (SENSE), for
his/her consistent encouragement and valuable guidance offered to us in a pleasant
manner throughout the course of the project work.

We sincerely express our gratitude to \textbf{Dr.~Ravi Sankar~A}, Dean, SENSE;
\textbf{Dr.~Mohanaprasad~K}, Associate Dean (Academics), SENSE; and
\textbf{Dr.~Chitra~K}, Associate Dean (Research), SENSE, for providing the necessary
facilities and for their constant encouragement and support throughout our project.

We also extend our heartfelt thanks to \textbf{Dr.~Jagannath~M}, Head of the
Department, for his continuous guidance and support during the course of this project.

We also take this opportunity to thank all the faculty of the School for their support
and their wisdom imparted to us throughout the course.

We thank our parents, family, and friends for bearing with us throughout the course of
our project and for the opportunity they provided us in undergoing this course in such
a prestigious institution.
}

\clearpage

%% ----------------------------------------------------------------
%% TABLE OF CONTENTS / LIST OF FIGURES / LIST OF TABLES
%% ----------------------------------------------------------------
\pagestyle{fancy}

\lhead{\emph{Contents}}
\tableofcontents

\lhead{\emph{List of Figures}}
\listoffigures

\lhead{\emph{List of Tables}}
\listoftables

%% ----------------------------------------------------------------
%% LIST OF ACRONYMS
%% ----------------------------------------------------------------
\lhead{\emph{List of Acronyms}}
\phantomsection
\addtotoc{List of Acronyms}
\chapter*{List of Acronyms}

\begin{acronym}[FreeRTOS]
  \acro{ISAC}    {Integrated Sensing and Communication}
  \acro{FMCW}    {Frequency Modulated Continuous Wave}
  \acro{FTM}     {Fine Time Measurement}
  \acro{DCI}     {Dynamic Covariance Intersection}
  \acro{MLP}     {Multi-Layer Perceptron}
  \acro{AoI}     {Age of Information}
  \acro{CI}      {Covariance Intersection}
  \acro{RTOS}    {Real-Time Operating System}
  \acro{UART}    {Universal Asynchronous Receiver-Transmitter}
  \acro{SRAM}    {Static Random-Access Memory}
  \acro{RCS}     {Radar Cross Section}
  \acro{RTT}     {Round-Trip Time}
  \acro{FOV}     {Field of View}
  \acro{LOS}     {Line of Sight}
  \acro{NLOS}    {Non-Line of Sight}
  \acro{MSE}     {Mean Squared Error}
  \acro{MAE}     {Mean Absolute Error}
  \acro{FFT}     {Fast Fourier Transform}
  \acro{MAC}     {Media Access Control}
  \acro{ISM}     {Industrial, Scientific and Medical}
  \acro{SDR}     {Software Defined Radio}
  \acro{CV}      {Constant Velocity}
  \acro{FOH}     {First Order Hold}
  \acro{ZOH}     {Zero Order Hold}
  \acro{EMA}     {Exponential Moving Average}
  \acro{IoT}     {Internet of Things}
  \acro{ML}      {Machine Learning}
  \acro{AI}      {Artificial Intelligence}
  \acro{GPS}     {Global Positioning System}
  \acro{IMU}     {Inertial Measurement Unit}
  \acro{LiDAR}   {Light Detection and Ranging}
\end{acronym}

\clearpage

\setstretch{1.15}
\pagestyle{empty}
\addtocontents{toc}{\vspace{2em}}

%% ----------------------------------------------------------------
\mainmatter
\pagestyle{fancy}

\input{Chapter1}   % Introduction
\input{Chapter2}   % Literature Survey
\input{Chapter3}   % System Design & Architecture
\input{Chapter4}   % Methodology
\input{Chapter5}   % Empirical Sensor Accuracy Evaluation
\input{Chapter6}   % Results and Discussion
\input{Chapter7}   % Challenges and Solutions
\input{Chapter8}   % Conclusion and Future Work
\input{Bibliography}

\addtocontents{toc}{\vspace{2em}}

\end{document}
