%% ----------------------------------------------------------------
%% Mapping of Sustainable Development Goals (SDGs)
%% ----------------------------------------------------------------
\phantomsection
\addtotoc{Mapping of Sustainable Development Goals}
\chapter*{Mapping of Sustainable Development Goals (SDGs)}
\thispagestyle{plain}

\vspace{0.5cm}

\noindent
\begin{longtable}{@{}|p{3.8cm}|p{5.2cm}|p{5.2cm}|@{}}
\hline
\rowcolor[gray]{0.85}
\textbf{Mapped SDGs} & \textbf{Justification} & \textbf{Example Impact} \\
\hline
\endfirsthead

\hline
\rowcolor[gray]{0.85}
\textbf{Mapped SDGs} & \textbf{Justification} & \textbf{Example Impact} \\
\hline
\endhead

\textbf{SDG 9 -- Industry, Innovation and Infrastructure} &
This project introduces a cost-effective two tier method to enable both sensing and communication through ISAC by making use of low-cost microcontrollers rather than expensive SDRs. &
Promotes the development of accessible, intelligent infrastructure and advanced tracking systems for commercial and industrial deployments. \\
\hline

\textbf{SDG 11 -- Sustainable Cities and Communities} &
This project has demonstrated successful continuous tracking in GPS denied interior environments through providing reliable operation while mitigating line-of-sight occlusion failures when transitioning to Wi-Fi FTM fallback. &
Improves safety and operational performance in many urban infrastructure applications including smart buildings, first responders, etc.\ and secure asset protection. \\
\hline

\textbf{SDG 12 -- Responsible Consumption and Production} &
Rather than relying on resource-intensive computing architectures this project utilizes low power edge devices (ESP32-S3) and algorithms (DCI + lightweight 11.6~KB Edge MLP) in order to minimize hardware footprint, energy usage, and electronic waste from large-scale deployment of complex networks of multi-modal sensor fusion. &
Reduces overall environmental impact and promotes sustainable hardware practices in IoT and sensor network deployments. \\
\hline

\textbf{SDG 3 -- Good Health and Well-being} &
The 24~GHz FMCW Radar has proven capable of obtaining fine detail micro-Doppler signatures of individuals including their respiratory motion during ``Statue Mode'' events. &
Enables high-level privacy preserving indoor monitoring capabilities to be used in applications such as elderly care, fall detection, etc.\ without the need for cameras. \\
\hline

\end{longtable}
